### 2013-07-04 cws/emnlp_cws/conclusion.tex
more updates

In this paper we presented ... blah blah.
Stress the simplicity and effectiveness of our method.

>>>>

In this paper we presented a straightforward approach to Chinese word segmentation using dual decomposition for system combination. We demonstrated that this method allows for joint decoding of existing CWS systems that performs better than either system alone on standard datasets for the task, and

We also demonstrated that our joint system produces more consistent segmentations than our baselines, a property that has potentially important downstream impacts for many Chinese NLP tasks. It remains to

### 2013-07-04 cws/emnlp_cws/discussion.tex
more updates

as crf
0.0428091404101
as pct
0.0441475626702
as dd
0.042168035925
cityu crf
0.0946373294134
cityu pct
0.10025983369
cityu dd
0.0867128300158
ctb crf
0.174004652166
ctb pct
0.18632727645
ctb dd
0.165767655651
pku crf
0.0423983535204
pku pct
0.0543269973345
pku dd
0.045000565176

@@

as crf
0.0718479895225
as pct
0.0681887138263
as dd
0.0624082516494
cityu crf
0.0660880615807
cityu pct
0.0742624297
cityu dd
0.0627869624389
msr crf
0.0755273737469
msr pct
0.064051889613
msr dd
0.0558050161967
pku crf
0.0892311495453
pku pct
0.0998921318846
pku dd
0.0868198134889

@@

Scoring Oracle Output, Sighan 2003
for as
	sighan2005/as.oracle	1855	726	9980	12561	122610	123739	0.913	0.904	0.908	0.043	0.722	0.921
for cityu
	sighan2005/cityu.oracle	577	371	3038	3986	40936	41142	0.917	0.912	0.914	0.074	0.817	0.925
for msr // currently broken
	sighan2005/msr.oracle	81	107	1066	1254	10987	10961	0.893	0.895	0.894	0.025	0.584	0.901
for pku
	sighan2005/pku.oracle	800	1661	9646	12107	104372	103511	0.892	0.899	0.895	0.058	0.815	0.896

>>>>

as crf
0.037814800237
as pct
0.038997075095
as dd
0.0372484903836
cityu crf
0.0923886605473
cityu pct
0.097496193366
cityu dd
0.0843064189868
ctb crf
0.170532711404
ctb pct
0.181993909505
ctb dd
0.161722439818
pku crf
0.0429803512049
pku pct
0.0552572297562
pku dd
0.0460509973844

@@

as crf
0.0635314146511
as pct
0.0603263902622
as dd
0.055097582491
cityu crf
0.0649537861096
cityu pct
0.0730776631941
cityu dd
0.0618197636595
msr crf
0.073782773985
msr pct
0.0628241148726
msr dd
0.054883418641
pku crf
0.0888607888366
pku pct
0.0996634383663
pku dd
0.086635535204

@@

Scoring Oracle Output, Sighan 2005
for as
	sighan2005/as.oracle	1855	726	9980	12561	122610	123739	0.913	0.904	0.908	0.043	0.722	0.921
for cityu
	sighan2005/cityu.oracle	577	371	3038	3986	40936	41142	0.917	0.912	0.914	0.074	0.817	0.925
for msr // currently broken
	sighan2005/msr.oracle	81	107	1066	1254	10987	10961	0.893	0.895	0.894	0.025	0.584	0.901
for pku
	sighan2005/pku.oracle	800	1661	9646	12107	104372	103511	0.892	0.899	0.895	0.058	0.815	0.896

### 2013-07-04 cws/emnlp_cws/experiment.tex
more updates

Give URL for the Stanford CRF segmenter. The perceptron-based word segmenter is a re-implementation of \cite{Zhang:2007:ACL}.
For development data, we used:
Training: CTB section 1-270  400-931 1001-115;   Dev: CTB section 271-300.

Hyper-parameters tuned on the dev set.
Perceptron: 10 iterations of training. 
CRF: L2-regularization Sigma set to 3.
Dual-decomp: initial step size set to 0.1, 100 iterations.

\subsection{Dataset}
Give description of the SIGHAN 2003 \cite{Sproat:2003:SIGHAN} and 2005 \cite{Emerson:2005:SIGHAN} bake-off datasets. 
List a table of the corpora names, size of training, testing, etc, similar to \cite{Sun:2010:COLING}.

>>>>

In this work, we employ two baseline models --- a character-based CRF and a word-based perceptron --- and test the performance of jointly decoding these baseline systems with dual decomposition.

For our character-based CRF, we use the open-source Stanford CRF segmenter described in \cite{Tseng:2005:SIGHAN}.\footnote{http://nlp.stanford.edu/software/segmenter.shtml} In this system we use L2 regularization with a value of X %TODO: insert actual value / word this properly
and sigma set to 3.

For our word-based perceptron, we use a reimplementation of \cite{Zhang:2007:ACL}, run with 10 iterations of training.

For joint decoding with dual decomposition, we use an initial step size set to 0.1, and run for 100 iterations.

% question: what is the relationship between this dev data and that used in sighan2003/2005?
We use the same development set employed by \cite{Zhang:2007:ACL}, with Chinese Treebank sections 1-270, 400-931, and 1001-115 used as training data and sections 271-300 used as development data for tuning the hyperparameters of all three systems.

\subsection{Datasets}
Our test data is the standard SIGHAN 2003 \cite{Sproat:2003:SIGHAN} and 2005 \cite{Emerson:2005:SIGHAN} bake-off datasets. [Add a note here about why not using CTB - who figured out it was broken, how do we know not to use it?]

%List a table of the corpora names, size of training, testing, etc, similar to \cite{Sun:2010:COLING}.

%
%\begin{table}
%\centering
%\begin{small}
%\begin{tabular}{ l | l | c | c | c | c | c   }
%%\cline{2-10}
%%\hline
%% &   \multicolumn{1}{|c}{Models} & \multicolumn{1}{c}{$\lambda$} & \multicolumn{1}{c|}{No. of experts} & {P} & {R} & {F$_1$}   & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{R} & \multicolumn{1}{c}{F$_1$}   \\
%\hline
%    \multicolumn{2}{c}{}  &  \multicolumn{1}{c}{\#W.T.} &  \multicolumn{1}{c}{\#W} &  \multicolumn{1}{c}{\#C.T.}    & \multicolumn{1}{c}{\#C}   &  \multicolumn{1}{c}{OOV}  \\ 
%\hline
%\multirow{4}{*}{2005}  & AS      & -  &  -  & -  &  - & 4.3   \\
%& MS      & 88K & 2.3M & 5K & 4.1M & 2.6 \\
%& PU      &  55k & 1.1M & 5K & 1.8M & 5.8  \\
%& CU      & 69K  & 1.5M& 5K & 2.4M & 7.4 \\
%\hline
%\multirow{3}{*}{2003} & AS  &  - & - & - & - & 2.2 \\
%& PU  &  - & - & - & - & 6.9 \\
%& CU  & - & - & - & - & 7.1  \\
%%\hline
%%\multirow{4}{*}{CTB}  &  Best03  &  \textbf{0.886}  & 0.875 &  \textbf{0.881} & 0.181 & 0.644  & \textbf{0.927} \\
%%& PcpTr       & 0.869 & 0.865 & 0.867 & 0.181 & 0.680  & 0.910 \\
%%& PcpTr & 0.865 & 0.871 & 0.868 & 0.181 & 0.660 & 0.910 \\
%%& DD  & 0.876 & \textbf{0.878} & 0.877 & 0.181 & \textbf{69.2} & 0.917  \\
%
%\end{tabular} 
%\caption{Results on SIGHAN 2005 and 2003 datasets. }\label{tbl:results}
%\end{small}
%\end{table}

### 2013-07-04 cws/emnlp_cws/introduction.tex
more updates

%Second paragraph talks about the challenges, specifically ambiguity and unknown words.
State-of-the-art performance in CWS is high, with F-scores in the upper 90s. %say this in a nicer way?
Still, challenges remain. Unknown words, also known as out-of-vocabulary (\textsc{oov}) words, lead to difficulties for word- or dictionary-based approaches.
Ambiguity can cause errors when the appropriate segmentation is determined contextually, such as 才能 (``talent") and 才 / 能 (``just able"). % from Gao acl 2003

%Third paragraph: 
There are two primary classes of models: character-based \cite{Xue:2003:IJCLCLP,Tseng:2005:SIGHAN,Zhang:2006:HLT-NAACL,Wang:2010:COLING} and word-based \cite{Andrew:2006:EMNLP,Zhang:2007:ACL}, with corresponding advantages and disadvantages. Character-based segmenters better model the internal compositional structure of words and are therefore more effective at detecting out-of-vocabulary words; however, they suffer from relative inconsistency. % problematic - our experiments show this isn't really true, the CRF is more consistent 6/8 times
Word-based segmenters are better at reproducing the words of the training lexicon and have a higher consistency, but are not as good at detecting \textsc{oov} words. Word-based models have the additional advantage that they tend to capture information from significantly larger contextual spans.
% too detailed?
%Due to the Markov assumption of the linear-chain CRFs that are commonly used in character-based segmentation the models typically only have information about the immediately neighboring characters, while word-based methods tend to capture information from significantly larger contextual spans.

@@

In this work, we propose a simple and principled joint decoding method for combining character-based and word-based segmenters based on dual decomposition. This method has strong optimality guarantees and works very well empirically. It is easy to implement and does not require retraining of existing character- and word-based segmenters.
Experimental results on standard SIGHAN 2003 and 2005 bake-off evaluations show that our model outperforms the character and word baselines by a significant margin on all 8 datasets. % wait, aren't we showing results for only 7?
In particular, it improves \textsc{oov} recall rates and consistency, % this is now validated
and gives the best reported results to date on 6 out of 7 datasets.

>>>>

%Second paragraph talks about the challenges, specifically ambiguity and unknown words.
State-of-the-art performance in CWS is high, with F-scores in the upper 90s. %say this in a nicer way?
Still, challenges remain. Unknown words, also known as out-of-vocabulary (\textsc{oov}) words, lead to difficulties for word- or dictionary-based approaches.
Ambiguity can cause errors when the appropriate segmentation is determined contextually, such as 才能 (``talent") and 才 / 能 (``just able") \cite{Gao:2003:ACL}.

%Third paragraph: 
There are two primary classes of models: character-based \cite{Xue:2003:IJCLCLP,Tseng:2005:SIGHAN,Zhang:2006:HLT-NAACL,Wang:2010:COLING} and word-based \cite{Andrew:2006:EMNLP,Zhang:2007:ACL}, with corresponding advantages and disadvantages. \cite{Sun:2010:COLING} details their theoretical distinctions: character-based approaches better model the internal compositional structure of words and are therefore more effective at inducing new out-of-vocabulary words; word-based approaches are better at reproducing the words of the training lexicon and can capture information from significantly larger contextual spans. Prior work has shown performance gains from combining these two types of models to exploit their respective strengths, but such approaches are often complex to implement and computationally expensive.

% too detailed?
%Due to the Markov assumption of the linear-chain CRFs that are commonly used in character-based segmentation the models typically only have information about the immediately neighboring characters, while word-based methods tend to capture information from significantly larger contextual spans.

@@

In this work, we propose a simple and principled joint decoding method for combining character-based and word-based segmenters based on dual decomposition. This method has strong optimality guarantees and works very well empirically. It is easy to implement and does not require retraining of existing character- and word-based segmenters.
Experimental results on standard SIGHAN 2003 and 2005 bake-off evaluations show that our model outperforms the character and word baselines by a significant margin.
In particular, it improves \textsc{oov} recall rates and segmentation consistency, % this is now validated
and gives the best reported results to date on 6 out of 7 datasets.

### 2013-07-04 cws/emnlp_cws/models.tex
more updates

\section{Char-based vs. Word-based Segmenters}

\subsection{Char-based models}
Describe models that treat CWS as a character sequence tagging task (first proposed by \cite{Xue:2003:IJCLCLP}), widely adopted and most commonly used these days.
Give the equation of CRF (see \cite{Tseng:2005:SIGHAN}). Briefly describe the features and point out how some of them can be expected to generalize well to OOV words (e.g. suffix and prefix features).

\subsection{Word-based models}
See \cite{Sun:2010:COLING} for a good description. We used the perceptron based model proposed by \cite{Zhang:2007:ACL}, give the equation of the perceptron, and describe the features. Point out how some of these features basically directly capture the training lexicon.

\subsection{Relative Strength and Weakness}
Char-based CRF models are better at generalizing over to OOV words (thus higher OOV recall).  (NOTE: 6 out of 8 datasets on test, CRF has better OOV recall, but we should defer to talk about this in the results section). But as a tradeoff, it generates more inconsistent segmentation, and creates lots of spurious words.
 The advantage of Word-based segmenters are that they are more consistent with the training lexicon, words seen in training lexicon are not likely to be segmented into many new ways; disadvantage is that it doesn't generalize well to OOV. Also exact inference is difficult, need to resolve to approximate decoding algorithms such as beam-searching.

>>>>

\section{Models for CWS}

In this section, we describe the character-based and word-based models we use as baselines, and review existing approaches to combine these models.

\subsection{Character-based Models}
In the most commonly used contemporary approach to character-based segmentation, first proposed by \cite{Xue:2003:IJCLCLP}, CWS is seen as a character sequence tagging task, where each character is tagged on whether it is at the beginning, middle, or end of a word. Conditional random fields (CRFs) are often used for this purpose (cite, cite, cite). In a CRF segmentation model, the probability of a label sequence is given by this equation:

%[add eq here]
% add defs of all the variables

Common linguistic features include character n-grams and morphological suffix/prefix features. Since these features capture information about the compositional properties of characters, they are likely to generalize well to unknown words.

\subsection{Word-based Models}

Initially word-based segmentation approaches employed simple heuristics like dictionary-lookup maximum matching \cite{Chen:1992:ACL}, contemporary approaches use machine learning techniques to solve an argmax problem of the form:

% add eq

The most successful such system reported to date is \cite{Zhang:2007:ACL}'s Perceptron-based model, which uses a search-based discriminative decoder to solve the ... %MQ add here?

%See \cite{Sun:2010:COLING} for a good description. We used the perceptron based model proposed by \cite{Zhang:2007:ACL}, give the equation of the perceptron, and describe the features. Point out how some of these features basically directly capture the training lexicon.
%
%\subsection{Relative Strength and Weakness}
%Char-based CRF models are better at generalizing over to OOV words (thus higher OOV recall).  (NOTE: 6 out of 8 datasets on test, CRF has better OOV recall, but we should defer to talk about this in the results section). But as a tradeoff, it generates more inconsistent segmentation, and creates lots of spurious words.
% The advantage of Word-based segmenters are that they are more consistent with the training lexicon, words seen in training lexicon are not likely to be segmented into many new ways; disadvantage is that it doesn't generalize well to OOV. Also exact inference is difficult, need to resolve to approximate decoding algorithms such as beam-searching.
%

\subsection{Mixing Models} Since the two types of models described above have different strengths and make different kinds of errors, various mixing approaches have been proposed to combine them \cite{Wang:2006:SIGHAN,Lin:2009:CICLing,Sun:2009:HLT-NAACL,Sun:2010:COLING,Wang:2010:COLING}.

\cite{Lin:2009:CICLing} and \cite{Wang:2006:SIGHAN} both incorporate a character-based Maxent local classifier model with a language model that captures more word-level context.
In order to bring in a bigram language model,  \shortcite{Lin:2009:CICLing} gave a heuristic decoding method that involves various forms of conditioning and back-off; \shortcite{Wang:2006:SIGHAN} gave a modified Viterbi algorithm with a complexity of $O(T^3)$.

\cite{Sun:2009:HLT-NAACL} presented a latent-variable model which obtains good performance, but it is very complicated to implement and difficult to train. 
\cite{Sun:2009:HLT-NAACL} use a method most similar to this work in that they also directly combine two segmenters -- one char-based and one word-based. However, they do it through segmenter bagging, which requires training 50 or more individual segmenters and polling their results at test time.

These mixing models perform well on standard datasets, but are not in wide use because of their high computational costs and difficulty of implementation.
